Features of Accretion Phase Gravitational Wave Emission from Two-dimensional Rotating Core-Collapse Supernovae

### 2019-03-27 ms.tex
paper updates

Furthermore, we recast our analysis by focusing on regions within the CCSN that emit GWs.  \textcolor{red}{[10]Figure \ref{fig:region} displays the GW strain emitted from the 20 $M_\odot$ progenitor from the inner 50 km (upper panel) and from the region between 50 km and 150 km (lower panel) of the supernova.  The upper panel shows an initial, low frequency signal, independent of rotation within the first 60 ms post bounce.  This signal is typically characterized by prompt convection \citep{mueller:1997}.}  The lower panel of Figure \ref{fig:region} displays the inhibited convective signal \textcolor{red}{($t_{pb} > 100$ ms)} with increasing rotation, as the GW signal in the gain region becomes increasingly muted.  \textcolor{red}{\st{The typical convective signals in the early post bounce regime are then quickly washed out by the post bounce ring down of the PNS, as rotation increases.}}

@@

Beyond the decreased prevalence of the peak frequency, an interesting trend emerges in Figure \ref{fig:spetra_long} as rotation increases.  
We separate the GW signals by region within the star.  The top row of Figure \ref{fig:spetra_long} corresponds to GWs originating from the inner 50 km of the supernova, and the GW signal in the bottom row originates from radial distances between 50 km and 150 km from the supernova center.
Focusing on the bottom row, we highlight a noticeable difference in the amplitude of the low frequency contributions, particularly around 40 Hz.  The nonrotating progenitors have undetectable low frequency signals for all three detectors, whereas rotating progenitors create measurable signals at low frequencies. 
This enhanced low-frequency signal may provide an observable feature that can help determine progenitor angular momentum information.

>>>>

Furthermore, we recast our analysis by focusing on regions within the CCSN that emit GWs.  The lower panel of Figure \ref{fig:region} displays the inhibited convective signal  with increasing rotation, as the GW signal in the gain region becomes increasingly muted.  The typical convective signals in the early post bounce regime are then quickly washed out by the post bounce ring down of the PNS, as rotation increases.

@@

Beyond the decreased prevalence of the peak frequency, an interesting trend emerges in Figure \ref{fig:spetra_long} as rotation increases.  
We separate the GW signals by region within the star.  The top row of Figure \ref{fig:spetra_long} corresponds to GWs originating from the inner 50 km of the supernova, and the GW signal in the bottom row originates from radial distances between 50 km and 150 km from the supernova center.  \textcolor{red}{[10]  In the top row, we note the first peak of emission, around 80 Hz, is independent of rotation.  We associate this with prompt convection that is strong enough to overcome the stabilizing effect of the positive specific angular momentum gradient.  We point to the bright, convective region in Figure \ref{fig:vaniso} within the first 25 ms post bounce that is present for all rotational velocities.}
Focusing on the bottom row, we highlight a noticeable difference in the amplitude of the low frequency contributions, particularly around 40 Hz.  The nonrotating progenitors have undetectable low frequency signals for all three detectors, whereas rotating progenitors create measurable signals at low frequencies. 
This enhanced low-frequency signal may provide an observable feature that can help determine progenitor angular momentum information.
